---
title: "Tutorial for R package QCwind"
author: "Jieyu Chen"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quality control procedure for citizen science wind observations using R package "QCwind"}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is the tutorial for implementing quality control procedure using the R package "QCwind". The quality control procedure is comprehensively introduced and discussed in the master thesis (\url{https://dspace.library.uu.nl/handle/1874/398742}), while this "QCwind" package is build to apply the QC checks.  

In this tutorial, we focus on the wind speed observations from citizen weather stations (CWS) located in the province of Utrecht of the Netherlands. The data is provided by Weather Observation Website (WOW-NL, \url{https://wow.knmi.nl/}), and we only take one-month data in 2017.01 as an example.   

```{r start, message=FALSE, include=FALSE}
# library(QCwind)
# load() # load date from this package
```

Firstly, let's have a look at the data structure:














